Errorless irrationality: removing error-driven components from the inverse base-rate effect paradigm

### 2023-01-05 docs/manuscript.tex
start experiment 2

One shortcoming of the current design is that participants can still make predictions about feature--category on a trial-by-trial basis.
Given that the general assumption is that diseases cause symptoms, participants could likely assume a causal link between symptoms and diseases.
This assumed causal relationship can encourage participants to make not an explicit (responding with the category label via the keyboard) but an implicit prediction.
Informally, participants might think of a certain feature--label causal relationship while reading the sentences.
People then resolve errors between the expected and the observed feature--label causality by allocating attention to rare features to distinguish diseases.
A simple solution is to remove any design component that makes it clear to participants what the category label is.
In addition, stimuli need to be constructed in a way that reduces the chance of people assuming any causal relationship between its features.

@@

In this experiment, we implemented the IBRE in a way most similar to memory experiments.

@@

Recruited 65 participants.

>>>>

One shortcoming of the current design is that participants can still make predictions about feature--category on a trial-by-trial basis.
Given that the general assumption is that diseases cause symptoms, participants could likely assume a causal link between symptoms and diseases.
This assumed causal relationship can encourage participants to make not an explicit (responding with the category label via the keyboard) but an implicit prediction.
Informally, participants might think of a certain feature--label causal relationship while reading the sentences.
People then resolve errors between the expected and the observed feature--label causality by allocating attention to rare features to distinguish diseases.

A simple solution is to remove any design component that makes it clear to participants what the category label is.
In addition, stimuli need to be constructed in a way that reduces the chance of people assuming any causal relationship between its features.

@@

In this experiment, we implemented the IBRE in a way most similar to cued-recall memory tasks.
Previous category labels were treated as features.
And features were selected to be solid black geometric shapes.
The task asked participants to memorise the arrangement of these shapes.
On each trial, we randomised the position of the geometric shapes in the arrangement.
This further minimised the chances of having any design component suggesting which feature is the category label.

@@

We recruited 65 undergraduate students who completed the exeriment for partial course credit.
Recruitment was done via the SONA recruitment system.
